Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-10-21 aa workingdraft/draft.tex
Done with param table

\begin{table}[H]
\caption{Experimental and natural parameter ranges. Natural values are approximations from other studies \cite{Nepf_2012,kadlec1990, czuba2015sedgravity}. Asterisk marks where empirical estimates \cite{mckenzie2008size} replace missing study-specific data.}
\centering
\begin{tabular}{lcccc}
\toprule
\textbf{Parameter}&\textbf{This study}&\textbf{Fauria et al. (2015)}&\textbf{Purich (2006)}&\textbf{Natural}\\
\midrule
Flow velocity (\SI{}{\centi\metre/\second})     
& 2.0--6.0    & 1.8--6.1    & 1.0--10.2    & 0--25     \\
Flow depth (\SI{}{\centi\metre})                
& 40          & 14--17      & 12           & 0--50     \\
\midrule
Collector diameter (\SI{}{\centi\metre})
& 0.318       & 0.3         & 0.63         & 0.1--1    \\
Collector Reynolds number                       
& 66--200     & 54--183     & 70--640      & 5--1000   \\ 
Collector density ($\#/m^2$)
&&&&\\
Frontal area density, $a$ (\SI{}{\per\meter})
&&&&\\ 
Solid volume fraction, $\phi_c$ 
&&&&\\ 
\midrule
Specific gravity      
& 1.53        &2.27--2.61*  & 1.03        & 2.56--2.87 \\
Particle diameter (\SI{}{\micro\metre})     
& 0.7--300    &1.25--250    & 212--250    &            \\
Suspended concentration (\SI{}{\micro\liter/\liter})      
&&&&\\
\midrule
Particle-collector diameter ratio, $R$      
&&&&\\
\bottomrule
\label{tbl:parameters}
\end{tabular}
\end{table}

\begin{table}[H]
\caption{Comparing experimental equipment.}
\centering
\begin{tabular}{lcccc}
\toprule
\textbf{Parameter}&\textbf{This study}&\textbf{Fauria et al. (2015)}&\textbf{Purich (2006)}&\textbf{Natural}\\
\midrule
Collector type
& greased cylinders & artificial leaves  & greased cylinders & e.g., stems, leaves \\ 
Particle type
& walnut shell flour  & road dust  & Pliolite particles   & e.g., silt, clay \\ 
\bottomrule
\label{tbl:leftoverparams}
\end{tabular}
\end{table}

>>>>

\begin{table}[H]
\caption{Experimental and natural parameter ranges. Natural values are based on approximations or measurements from cited studies and literature reviews.}
\begin{threeparttable}
\centering
\begin{tabular}{lcccc}
\toprule
\textbf{Parameter}&\textbf{This study}&\textbf{Fauria et al. (2015)}&\textbf{Purich (2006)}&\textbf{Natural}\\
\midrule
Flow velocity (\SI{}{\centi\metre/\second})     
& 2.0--6.0    & 1.8--6.1    & 1.0--10.2    & 0--25 \cite{nikora2008hydraulic}    \\
Flow depth (\SI{}{\centi\metre})                
& 40          & 14--17      & 12           & 0--50 \cite{kadlec1990}    \\
\midrule
Collector shape
& Cylindrical & Artificial grass  & Cylindrical & --- \\ 
Collector diameter (\SI{}{\centi\metre})
& 0.318       & 0.3         & 0.6          & 0.1--1.2 \cite{Nepf_2012,wright2018hydrological} \\
Collector Reynolds number                       
& 66--200     & 54--183     & 70--640      & 5--1000 \cite{kadlec1990}  \\ 
Collector density ($\#/\text{m}^2$)
& 278--1450   & 2724--7209  & 1013--4053   & 10--2700 \cite{wright2018hydrological} \\
Solid volume fraction (\%)
& 0.22--1.17  & 0.82--2.16  & 2.86--11.5   & 0.1--45 \cite{Nepf_2012} \\ 
\midrule
Particle type
& Walnut shell flour  & Road dust  & Pliolite\textsuperscript{\textregistered}   & --- \\ 
Specific gravity      
& 1.53        &2.27--2.61 \tnote{1}  & 1.03         & 2.56--2.87 \cite{czuba2015sedgravity} \\
Average particle diameter, $d_{50}$ (\SI{}{\micro\metre})     
& 25.2        & $\sim$10--15      & 212--250     & 45--100 \cite{hejduk2010variations,noe2010glades}  \\
Suspended concentration (\SI{}{\micro\liter/\liter})      
& 5.3--53.8   & 9--50       & $\sim$110   & 2-25 \cite{noe2010glades,aiona2013can}      \\
\midrule
Particle-collector diameter ratio, $R$      
&0.0079       &0.0004--0.083 \tnote{2} & 0.037        & <0.25     \\
\bottomrule
\label{tbl:parameters}
\vspace{-4mm}
\end{tabular}
\begin{tablenotes}
\footnotesize \item[1] Estimates from an observational study about road dust \cite{mckenzie2008size} (study-specific data unavailable)
\vspace{2mm}
\footnotesize \item[2] Fauria et al. (2015) used a LISST to measure collection across a broad range of particle diameters (1.25--250 \SI{}{\micro\metre})
\end{tablenotes}
\end{threeparttable}
\end{table}
